New orbits of irregular satellites designed for the predictions of stellar occultations up to 2020, based on thousands of new observations

### 2016-07-04 Irregular-occ/Irregular-occ.tex
.

\documentclass[useAMS,usenatbib]{mn2e}
\usepackage[brazilian,english]{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{times}  %%% needed to embed font 1 text
\usepackage{prettyref}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{epstopdf}
\usepackage{color}
\usepackage[breaklinks=true, draft]{hyperref}  % draft because there is an error = 'pdfTeX error (ext4): \pdfendlink ended up in different nesting level than \pdfstartlink'.
\usepackage{arydshln} % creates horizontal dashed lines in tables

@@

\title[Orbits and predictions for occultations up to 2020]{New orbits of irregular satellites designed for the predictions of stellar occultations up to 2020, based on thousands of new observations}
%\title[Orbits and predictions for occultations up to 2020]{New orbits of irregular satellites based on thousands of new observations and predictions for stellar occultations up to 2020}
\author[A. R. Gomes-J\'unior, M. Assafin, L. Beauvalet et al.]{A. R. Gomes-J\'unior$^{1}$\thanks{E-mail: altair08@astro.ufrj.br},
M. Assafin$^{1,\dag}$,
L. Beauvalet$^{2,3}$,
J. Desmars$^{4}$,\newauthor
R. Vieira-Martins$^{1,2,5,\dag}$,
J. I. B. Camargo$^{2,5}$,
B. E. Morgado$^{1,2}$
F. Braga-Ribas$^{2,6}$
\\
$^{1}$Observat\'orio do Valongo/UFRJ, Ladeira Pedro Ant\^onio 43,
CEP 20.080-090 Rio de Janeiro - RJ, Brazil\\
$^{2}$Observat\'orio Nacional/MCTI, R. General Jos\'e Cristino 77, CEP 20921-400 Rio de Janeiro - RJ, Brazil\\
$^{3}$Observatoire de Paris/SYRTE, 77 Avenue Denfert Rochereau 75014 Paris, France\\
$^{4}$Institut de m\'ecanique c\'eleste et de calcul des \'eph\'em\'erides - Observatoire de Paris, UMR 8028 du CNRS, 77 Av. Denfert-Rochereau,\\ 75014 Paris, France\\
$^{5}$Laborat\'orio Interinstitucional de e-Astronomia - LIneA, Rua Gal. Jos\'e Cristino 77, Rio de Janeiro, RJ 20921-400, Brazil\\
$^{6}$Federal University of Technology - Paran\'a (UTFPR / DAFIS), Rua Sete de Setembro, 3165, CEP 80230-901, Curitiba, PR, Brazil\\
$^\dag$Affiliated researcher at Observatoire de Paris/IMCCE, 77 Avenue Denfert Rochereau 75014 Paris, France
}
\begin{document}
\newcommand{\noccs}{5442 } % total number of occultations
\defcitealias{GomesJunior2015}{GJ15}

@@

ARG-J thanks the financial support of CAPES.
MA thanks the CNPq (Grants 473002/2013-2 and 308721/2011-0) and FAPERJ (Grant E-26/111.488/2013).
RV-M thanks grants: CNPq-306885/2013, Capes/Cofecub-2506/2015, Faperj/PAPDRJ-45/2013.
JIBC acknowledges CNPq for a PQ2 fellowship (process number 308489/2013-6).
BEM thanks the financial support of CAPES.
FB-R acknowledges PAPDRJ-FAPERJ/CAPES E-43/2013 number 144997, E-26/101.375/2014.
The numerical model of the satellites of Jupiter was developped during a post-doctoral contract funded by the Chinese Academy of Sciences (CAS) and supported by the National Scientific Fund of China (NSFC). \textbf{The authors thank Dr. Nikolay Emelyanov for his comments to improve the paper.}

>>>>

\documentclass[useAMS,usenatbib]{mn2e}
\usepackage[brazilian,english]{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{times}  %%% needed to embed font 1 text
\usepackage{prettyref}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{epstopdf}
\usepackage{color}
\usepackage[breaklinks=true]{hyperref}  % draft because there is an error = 'pdfTeX error (ext4): \pdfendlink ended up in different nesting level than \pdfstartlink'.
\usepackage{arydshln} % creates horizontal dashed lines in tables

@@

\title[Orbits and predictions for occultations up to 2020]{New orbits of irregular satellites designed for the predictions of stellar occultations up to 2020, based on thousands of new observations}
%\title[Orbits and predictions for occultations up to 2020]{New orbits of irregular satellites based on thousands of new observations and predictions for stellar occultations up to 2020}
\author[A. R. Gomes-J\'unior, M. Assafin, L. Beauvalet et al.]{A. R. Gomes-J\'unior$^{1}$\thanks{E-mail: altair08@astro.ufrj.br},
M. Assafin$^{1,\dag}$,
L. Beauvalet$^{2,3}$,
J. Desmars$^{4}$,\newauthor
R. Vieira-Martins$^{1,2,5,\dag}$,
J. I. B. Camargo$^{2,5}$,
B. E. Morgado$^{1,2}$
F. Braga-Ribas$^{2,6}$
\\
$^{1}$Observat\'orio do Valongo/UFRJ, Ladeira Pedro Ant\^onio 43,
CEP 20.080-090 Rio de Janeiro - RJ, Brazil\\,
$^{2}$Observat\'orio Nacional/MCTI, R. General Jos\'e Cristino 77, CEP 20921-400 Rio de Janeiro - RJ, Brazil\\
$^{3}$Observatoire de Paris/SYRTE, 77 Avenue Denfert Rochereau 75014 Paris, France\\
$^{4}$IMCCE, Observatoire de Paris, PSL Research University, CNRS, Sorbonne Universités, UPMC Univ Paris 06, Univ. Lille, 77 Av. Denfert-Rochereau, 75014 Paris, France\\
$^{5}$Laborat\'orio Interinstitucional de e-Astronomia - LIneA, Rua Gal. Jos\'e Cristino 77, Rio de Janeiro, RJ 20921-400, Brazil\\
$^{6}$Federal University of Technology - Paran\'a (UTFPR / DAFIS), Rua Sete de Setembro, 3165, CEP 80230-901, Curitiba, PR, Brazil\\
$^\dag$Affiliated researcher at Observatoire de Paris/IMCCE, 77 Avenue Denfert Rochereau 75014 Paris, France
}
\begin{document}
\newcommand{\noccs}{5442 } % total number of occultations
\defcitealias{GomesJunior2015}{GJ15}

@@

ARG-J thanks the financial support of CAPES.
MA thanks the CNPq (Grants 473002/2013-2 and 308721/2011-0) and FAPERJ (Grant E-26/111.488/2013).
RV-M thanks grants: CNPq-306885/2013, Capes/Cofecub-2506/2015, Faperj: PAPDRJ-45/2013 and Cient.Est-05/2015.
JIBC acknowledges CNPq for a PQ2 fellowship (process number 308489/2013-6).
BEM thanks the financial support of CAPES.
FB-R acknowledges PAPDRJ-FAPERJ/CAPES E-43/2013 number 144997, E-26/101.375/2014.
The numerical model of the satellites of Jupiter was developped during a post-doctoral contract funded by the Chinese Academy of Sciences (CAS) and supported by the National Scientific Fund of China (NSFC).
\textbf{The authors thank Dr. Nikolay Emelyanov for his comments to improve the paper.}
